A general model of microbial interactions in a chemostat

### 2019-12-12 tex/Tracking.tex
changes in tex

The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110}
	\caption{Simulation applying the control strategy.}
	\label{ControlSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{260919_Try1_AOB_Iter_110}
	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
	\label{AOBSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{260919_Try1_NOB_Iter_110}
	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
	\label{NOB Simulation}
\end{figure}

One can observe that in figure \ref{ControlSimulation} the predicted $s_3$ around day 240 is much higher than the measurement.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_AOB_Iter_110}
	\caption{Control obtained for OTU in $G_1$ (AOB).}
	\label{AOB_control}
	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_NOB_Iter_110}
	\caption{Control obtained for OTU in $G_2$ (NOB).}
	\label{NOB_control}
\end{figure}

>>>>

The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_metabolites_Iter_10}
	\caption{Simulation applying the control strategy.}
	\label{ControlSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_AOB_Iter_10}
	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
	\label{AOBSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_NOB_Iter_10}
	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
	\label{NOB Simulation}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_AOB_Iter_10}
	\caption{Control obtained for OTU in $G_1$ (AOB).}
	\label{AOB_control}
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_NOB_Iter_10}
	\caption{Control obtained for OTU in $G_2$ (NOB).}
	\label{NOB_control}
\end{figure}
